### 2025-07-11 cognitive-bias.qmd
20250710 - quotes
20250711 - replacement of video content for PDF/ePub

@@

> "Hindsight is 20/20." – Idiom

@@

> "The more you know, the more you know you don't know." – Anonymous

>>>>

::: {.content-visible unless-format="html:js"}

@GetUpESPN2021 provides a video (archived at <https://perma.cc/JW8E-KV2C>) of Kyle Pitts drawing comparisons to the LeBron James of Tight Ends.

@@

> "*Hindsight is 20/20.*" – Idiom

@@

> "*The more you know, the more you know you don't know.*" – Anonymous

### 2025-07-11 sports-cognitive-psychology.qmd
20250711 - replacement of video content for PDF/ePub

As an example of people dismissing analytics, @fig-football-commentator is a [2015 video clip](https://streamable.com/1hw8) of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops" [@ABC2015].
His characterization suggests he believes that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.
The full game is [here](https://www.youtube.com/watch?v=1L9D2rp0mk8) [@ABC2015a].

@@

>>>>

As an example of people dismissing analytics, @fig-football-commentator is a [2015 video clip](https://streamable.com/1hw8) of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops" [@ABC2015].
His characterization suggests he believes that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.
The full game is available to watch [here](https://www.youtube.com/watch?v=1L9D2rp0mk8) [@ABC2015a].

@@

::: {.content-visible unless-format="html:js"}

As an example of people dismissing analytics, there is a 2015 video clip of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops" [@ABC2015].
His characterization suggests he believes that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.
The full game is available to watch here: <https://www.youtube.com/watch?v=1L9D2rp0mk8> [@ABC2015a].
